---
title: "dable and flextable"
output:
  rmarkdown::html_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{dable-flextable}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r "SETUP", include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>")
library(flextable)
library(dable)
## devtools::load_all()
dpset_defaults(overwrite = TRUE)
if(FALSE){
    .cmp <- function() rmarkdown::render(input = "vignettes/dable-and-flextable.Rmd")
    .look <- function() shell.exec("dable-and-flextable.html")
}
```

# About

This is a document to test the `dable2flextable` functions in the `dable`
package. To learn about the `dable` package, see the *dable manual* vignette.


Setup for testing:

```{r}
d <- test_data()
g <- dguide(d, id = "id", vtab = test_vtab(), stab = test_stab(), catg.tol = 15)
```

# Showcase

This section showcases some standard usage.

## Baseline theme 0

```{r, message = FALSE}
dt <- baseline(d, theme = 0, guide = g, gtab = "area", time.unit = 365.25,
               part = list(T,T,T))
blextable(dt)
```
## Baseline theme 2

```{r, message = FALSE}
dt <- baseline(d, theme = 2, guide = g, gtab = "area", time.unit = 365.25,
               part = list(T,T,T))
blextable(dt)
```


# Tests

This section tests the `dable2flextable` functions in `dable`; it contains lots
of permutations of the arguments to see if it all goes through.

## Simple descriptive tables

```{r, message = FALSE}
dreal(d) |> dextable()
dreal(d, guide = g) |> dextable()
dreal(d, guide = g) |> dextable(row.group = FALSE)
dreal(d, guide = g) |> dextable(t2l = FALSE, row.group = FALSE)
dreal(d, guide = g, gtab = "gender", part = c(T,T,T)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(T,T,F)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(T,F,T)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(F,T,F)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(T,F,F)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(F,T,F)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(F,F,T)) |> dextable()
dreal(d, guide = g, gtab = "gender", part = c(F,F,F))
dreal(d, guide = g, gtab = "gender") |> dextable(row.group = FALSE)
dreal(d, guide = g, gtab = "gender") |> dextable(t2l = FALSE, row.group = FALSE)
```

## Baseline tables

To appear.
